---
title: 'Assignment #4'
author: "Cho Kim"
date: "February 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

#### FiveThirtyEight Data (30 points): Navigate on GitHub to https://github.com/rudeboybert/fivethirtyeight and read README.md. Seriously, it will include everything you need. 

* Install the fivethirtyeight package.
* In the listing of Data sets in package ‘fivethirtyeight,’ assign the eighteenth data set to an object ‘df.’

```{r 1, echo=TRUE}
#install.packages("devtools")
#install.packages("fivethirtyeight")
library(fivethirtyeight)
df <- data.frame(college_recent_grads)
```

* Use a more detailed list of the data sets to write out the URL in a comment to the related news story.
```{r 1 link, echo=TRUE}
vignette("fivethirtyeight", package = "fivethirtyeight")
#http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/
#FiveThirtyEight's guide to picking a college major.
```

* Using R command(s), give the dimensions and column names of this data frame.
```{r 1 dim, echo=TRUE}
dim(df)
str(df)
colnames(df)
```
